Learning constraints in tabular data

### 2016-05-20 Paper/ECAI/tabular.tex
minor

\paragraph{Dependencies}
\sergey{question: the guidlines say caption for tables above the tables, but dsaa papers from 2015 (I have checked two) put it below, that's confusing...}
In Table~\ref{table:constraints} one can see that for some constraints we used the predicate of another constraint in its signature, e.g. for \textit{PERMUTATION}. This expresses a dependency of the constraint on that other constraint. This can be interpreted as follows: the signature of the constraint consists of its own signature plus the signature of the depending constraint, and its definition of its own definition plus the definition of the depending constraint.
In FOL, we can see that one constraint entails the other, for example if $\ecperm{\sg_x}$ holds for a block $\sg_x$, then $\ecalldiff{\sg_{x}}$ also holds.

>>>>

\paragraph{Dependencies}
\sergey{question: the guidlines say caption for tables above the tables, but dsaa papers from 2014 and 2015 (I have checked three) put it below, that's confusing...}
In Table~\ref{table:constraints} one can see that for some constraints we used the predicate of another constraint in its signature, e.g. for \textit{PERMUTATION}. This expresses a dependency of the constraint on that other constraint. This can be interpreted as follows: the signature of the constraint consists of its own signature plus the signature of the depending constraint, and its definition of its own definition plus the definition of the depending constraint.
In FOL, we can see that one constraint entails the other, for example if $\ecperm{\sg_x}$ holds for a block $\sg_x$, then $\ecalldiff{\sg_{x}}$ also holds.
